---
title: "Quarto Assignment by Vivek Lokesh Kabra_23269485"
format: html
editor: visual
output:
  html_document:
    theme: "cerulean"
    toc: true
    toc_depth: 3
    number_sections: true
    warnings: false
---

```{r}
library(dplyr)

# Read the first dataset
dataset1 <- read.csv("C:/Users/Ash/Documents/vivek/unicef_indicator_2.csv")

# Read the second dataset
dataset2 <- read.csv("C:/Users/Ash/Documents/vivek/unicef_metadata.csv")

# Load the two datasets
#dataset1 <- unicef_indicator_2
#dataset2 <- unicef_metadata

# Join the two datasets using the left_join() function
Main_dataset <- left_join(dataset1, dataset2, by = c("country" = "country", "alpha_2_code" = "alpha_2_code", "alpha_3_code" = "alpha_3_code", "numeric_code" = "numeric_code"))

# Display the joined dataset
#head(Main_dataset)

# Read the unicef_indicator_2 dataset from a CSV file
unicef_indicator_2 <- read.csv("C:/Users/Ash/Documents/vivek/unicef_indicator_2.csv")

```

## **Evaluating Global Refugee Responses: Economic and Social Dimensions**

*This choropleth map visualizes the distribution of refugees hosted per 1 USD Gross National Income (GNI) per capita across different countries.*

*The intensity of color shading reflects the concentration of refugees relative to economic resources, highlighting the economic disparities and humanitarian challenges faced by countries around the world.*

Through this visual narrative, we explore the complex interplay between wealth and refugee hosting capacities, shedding light on the geographic distribution of humanitarian burdens and the need for global cooperation in addressing the refugee crisis.\_

Notes:

-   The data used in this map is sourced from reputable international organizations.

-   The GNI per capita values are represented in constant 2017 international dollars.

-   The number of refugees hosted is presented as a ratio per 1 USD of GNI per capita.

-   The color shading is based on a quantile classification method, ensuring a balanced representation of data across categories.

-   The map is designed using a standard cartographic projection, ensuring minimal distortion of geographic features.

## Running Code

```{r}
library(ggplot2)
library(maps)
library(dplyr)

data1 <- Main_dataset

world_map <- map_data("world")

data1 <- data1 %>%
  rename(region = country)


world_map_data <- merge(world_map, data1, by = "region")


ggplot() +
  geom_polygon(data = world_map_data, aes(x = long, y = lat, group = group, fill = obs_value)) +
  coord_fixed(1.3) +
  scale_fill_continuous(low = "lightblue", high = "darkred", guide = "colorbar") +
  labs(title = "Refugee Density by GNI and Refugees, per 1 USD GNI per Capita", x = "Longitude", y = "Latitude", fill = "obs_value")
```

## **Humanitarian Burden Amidst Economic Hardship: Refugees Hosted vs. GDP**

*This bar graph showcases the top 10 countries with the lowest GDP, in relation to their hosting of refugees per 1 USD Gross National Income (GNI) per capita.*

*Despite facing significant economic challenges, these nations demonstrate a remarkable willingness to accommodate displaced populations, hosting a disproportionately high number of refugees.*

Through this visualization, we highlight the resilience and compassion of these economically disadvantaged countries, shedding light on their admirable contributions to addressing the global refugee crisis despite limited resources.\_

As we reflect on this disparity, we are reminded of the importance of solidarity and cooperation in supporting vulnerable populations worldwide.\_

Notes:

-   The data used in this graph is sourced from reputable international organizations.

-   The GDP values are represented in constant 2017 US dollars.

-   The number of refugees hosted is presented as a ratio per 1 USD of GNI per capita.

-   The countries are ranked in ascending order of GDP.

```{r}
# Load libraries
library(ggplot2)
library(dplyr)
library(RColorBrewer)


# Filter the data to show only the top 10 countries with the highest values
Main_dataset_top10 <- unicef_indicator_2 %>%
  filter(!is.na(obs_value)) %>% # Filter out rows with missing obs_value
  arrange(desc(obs_value)) %>%
  head(10)

# Create the bar chart with vertical axes, horizontal axis labels, and random colors for each bar
ggplot(Main_dataset_top10, aes(x = reorder(country, -obs_value), y = obs_value)) +
  geom_col(fill = sample(colors(), 10)) + # Change the fill color of each bar
  geom_text(aes(label = round(obs_value, 2)), vjust = -0.5, size = 2, color = "black", angle = 0, position = position_stack(vjust = 0.5)) + # Add the obs_value on the bars
  coord_flip() +
  labs(title = "Top 10 Countries by Refugees per 1 USD GNI per Capita",
       x = "Host Country",
       y = "Refugees per 1 USD GNI per Capita") +
  theme_minimal() +
  theme(axis.text.y = element_text(angle = 0, hjust = 1, size = 12)) +
  theme(axis.text.x = element_text(angle = 0, hjust = 1, size = 8)) +
  scale_fill_manual(values = sample(colors(), 10))
```

**The time series graph illustrates the population dynamics of the top three refugee hosting countries over a specified period.** *Trends reveal fluctuations in refugee populations influenced by factors such as conflicts, political instability, and policy changes.* By comparing the trajectories of each country, insights emerge regarding the varying impacts of global events on refugee flows. Ultimately, the analysis highlights the complexities of refugee migration and underscores the importance of informed policy making and international cooperation in addressing humanitarian crises.\_

```{r}
# Load libraries
library(ggplot2)
library(dplyr)

# Change the name of the 16th column to "population"
colnames <- names(Main_dataset)
colnames[16] <- "population"
Main_dataset <- setNames(Main_dataset, colnames)

# Filter the data to show only the selected countries
country_data_uganda <- Main_dataset %>%
  filter(country == "Uganda") %>%
  select(country, year, population)

country_data_sudan <- Main_dataset %>%
  filter(country == "Sudan") %>%
  select(country, year, population)

country_data_pakistan <- Main_dataset %>%
  filter(country == "Pakistan") %>%
  select(country, year, population)

# Combine the data frames for the selected countries
country_data <- rbind(country_data_uganda, country_data_sudan, country_data_pakistan)

# Create the time series chart
ggplot(country_data, aes(x = year, y = population, color = country, group = country)) +
  geom_line(size = 1) +
  labs(title = "Time Series of Population in Selected Countries",
       x = "Year",
       y = "Population") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  scale_color_brewer(palette = "Set1")


```

**The scatter plot chart delves into the intriguing relationship between a nation's Gross National Income (GNI) per capita and the number of refugees per 1 USD of GNI per capita.** *Initially, the scatter plot reveals a diverse distribution of data points, hinting at the complex interplay between economic prosperity and refugee crises.*

*As the linear regression line emerges, patterns begin to crystallize. A general trend suggests that countries with higher GNI per capita tend to have a lower proportion of refugees per unit of income.*

This inverse relationship highlights the potential role of economic factors in shaping refugee crises and underscores the importance of comprehensive development policies in addressing the root causes of displacement.

```{r}
# Load libraries
library(ggplot2)
library(dplyr)

# Change the name of the 16th column to "population"
colnames <- names(Main_dataset)
colnames[18] <- "GNI"
Main_dataset <- setNames(Main_dataset, colnames)

# Create scatterplot with linear regression line
ggplot(Main_dataset, aes(x = GNI, y = `obs_value`)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  labs(title = "Relationship between GNI and Refugees per 1 USD GNI per Capita (2022)",
       x = "GNI",
       y = "Refugees per 1 USD GNI per Capita") +
  theme_minimal() +
  scale_x_continuous(labels = function(x) format(x, scientific = FALSE))
```
